Optimizing the Robotics Closet

### 2018-12-12 paper.tex
turned it in!

Note about notation: ($l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the

@@

\item $\sum_{j = 1}^{m}w_{ij} L^{item}_j \leq L^{shelf}_i, $ for every $1 \leq i \leq n_0$ ($n_0 = $ number of shelves).

@@

\section{Solution and Results}
We used the Gurobi optimization library to solve the formulated integer programming
problem. The results placed 11 items into Shelf 5, 16 items into Shelf 6, 13 items
into Shelf 7, 13 items into Shelf 8, 11 items into Shelf 9, 2 into 10, 1 into 11,
2 into 12, and 11 into 13. The remaining shelves had no items placed in them.
This confirmed our intuition that there was plenty of space for the items
even with the single depth layer constraint. A brief examination of the items
allocated to each specific shelf provides support for validity of the model;
it is not difficult to imagine the items listed placed compactly, but plausibly.
\par
Only the shelves that have distance 2 (highest distance in the input data set)
are left empty. This is an indication that proximity is, in fact, taken into
account by the model. Finally, LiPo batteries are placed onto the same drawer,
as are NVIDIA Jetsons and other closely related items. This validates that the
connected components constraint is being considered.

@@

\section{References}
\begin{thebibliography}{9}
\bibitem{volleyball} Guido Cocchi, Alessandro Galligari, Federica Picca Nicolino,
  Veronica Piccialli, Fabio Schoen, Marco Sciandrone.
  “Scheduling the Italian National Volleyball Tournament.” Interfaces 48(3):271-284, 2018. 
\bibitem{india} Singh, Deepesh. “A Beginner’s guide to Shelf Space Optimization using
  Linear Programming.” Analytics Vidhya, 2016
\bibitem{knapsack} Andrea Lodi, Michele Monaci. “Integer Linear Programming Models for
  2-staged Two-Dimensional Knapsack Problems.” Dipartimento di Elettronica,
  Informatica e Sistemistica, University of Bologna, 2001
\bibitem{imnotamonkeyimascientist} Winston, Wayne. “Operations research:
  Applications and algorithms.” Belmont, CA: Thomson/Brooks/Cole, 2004
\bibitem{siggraph}  Yu, Lap-Fai, et al. “Make It Home.” ACM SIGGRAPH 2011 Papers
  on - SIGGRAPH 11, 2011, doi:10.1145/1964921.1964981.  
\end{thebibliography}
Source code can be found at: https://github.com/save-buffer/math381

\pagebreak
\newgeometry{left=3cm,right=3cm,top=3cm,bottom=3cm}
\section{Appendix: Solution Visualization}
\includegraphics[scale=0.40,angle=90]{image.png}
\end{document}

>>>>

Note about notation: ($L^{item}_k$ indicates the length of item $k$ while $L^{shelf}_k$ indicates the

@@

\item $\sum_{j = 1}^{m}w_{ij} L^{item}_j \leq L^{shelf}_i, $ for every $1 \leq i \leq n$ ($n = $ number of shelves, including stacking).

@@

\section{Solution and Results}
We used the Gurobi optimization library to solve the formulated integer programming
problem. The results placed 11 items into Shelf 5, 16 items into Shelf 6, 13 items
into Shelf 7, 13 items into Shelf 8, 11 items into Shelf 9, 2 into 10, 1 into 11,
2 into 12, and 11 into 13. The remaining shelves had no items placed in them.
This confirmed our intuition that there was plenty of space for the items
even with the single depth layer constraint. A brief examination of the items
allocated to each specific shelf provides support for validity of the model;
it is not difficult to imagine the items listed placed compactly, but plausibly.
\par
Only the shelves that have distance 2 (highest distance in the input data set)
are left empty. This is an indication that proximity is, in fact, taken into
account by the model. Finally, LiPo batteries are placed onto the same drawer,
as are NVIDIA Jetsons and other closely related items. This validates that the
connected components constraint is being considered. A visualization of our
result is included in the appendix.

@@

\pagebreak
\section{References}
\begin{thebibliography}{9}
\bibitem{volleyball} Guido Cocchi, Alessandro Galligari, Federica Picca Nicolino,
  Veronica Piccialli, Fabio Schoen, Marco Sciandrone.
  “Scheduling the Italian National Volleyball Tournament.” Interfaces 48(3):271-284, 2018. 
\bibitem{india} Singh, Deepesh. “A Beginner’s guide to Shelf Space Optimization using
  Linear Programming.” Analytics Vidhya, 2016
\bibitem{knapsack} Andrea Lodi, Michele Monaci. “Integer Linear Programming Models for
  2-staged Two-Dimensional Knapsack Problems.” Dipartimento di Elettronica,
  Informatica e Sistemistica, University of Bologna, 2001
\bibitem{imnotamonkeyimascientist} Winston, Wayne. “Operations research:
  Applications and algorithms.” Belmont, CA: Thomson/Brooks/Cole, 2004
\bibitem{siggraph}  Yu, Lap-Fai, et al. “Make It Home.” ACM SIGGRAPH 2011 Papers
  on - SIGGRAPH 11, 2011, doi:10.1145/1964921.1964981.  
\end{thebibliography}
Source code can be found at: https://github.com/save-buffer/math381

\pagebreak
\newgeometry{left=3cm,right=3cm,top=3cm,bottom=3cm}
\section{Appendix: Solution Visualization}
\includegraphics[scale=0.40,angle=90]{visualizer/image.png}
\end{document}
